---
title: "Movie Remakes"
author: "Mitchell Lisle"
date: "23/12/2017"
output: html_document
---

```{r setup, include=FALSE}
library(jsonlite)
library(tidyverse)
library(stringr)
library(highcharter)
library(DT)

source("R/processing.R")
source("R/visualisations.R")

allMovies <- read.csv("data/allMovies.csv", stringsAsFactors = FALSE)
movieMetaData <- data.table::fread("data/movieMetaData.csv", stringsAsFactors = FALSE)

originals <- allMovies %>% select(contains("originals")) %>% rename("year" = originals_year)
remakes <- allMovies %>% select(contains("remakes")) %>% rename("year" = remakes_year)

knitr::opts_chunk$set(echo = FALSE)
```
### Data
This analysis was made for [this reddit thread](https://www.reddit.com/r/DataVizRequests/comments/7irlb9/request_i_would_like_for_someone_to_visualize/). The data source for this analysis was taken from [Wikipedia](https://en.wikipedia.org/wiki/Lists_of_film_remakes).

### Years of the most remakes
The original question this analysis was endeavouring to answer was, 'How have remakes of old moves been trending over time?'. To answer this, I obtained the data from the above Wikipedia page and then looked at the movies that are classed as remakes; i.e Movies that were released after an original movie of the same name/plot. This data doesn't take into account movies that were remakes of books, it is also not clear if the data obtained is a comprehensive or exhaustive list. However, it does give some insight into the trend of movie remakes.

As you can see from the chart below, there has been quite a ramp up in the number of movies that are remakes. We see an average of between ~5 to ~7 in the years from 1904 to around 1980. From 1980 things really start ramping up and we seek a peak of **28 movies** in 2005 being classed as remakes. Interestingly, in more recent years there has been a decline the number of remakes and a return to a more modest average of between ~6 to ~7. Perhaps the remake bubble is over? Maybe remakes started off performing well at the box office but now people are looking for more original content? Or perhaps we have oversatured previous decades original movies and there are little to no remakes left? Further analysis will help to answer these questions.



```{r}
remakesByYear <- countByYear(remakes)
countByYear_chart(remakesByYear, c("#CFCFCF", "#AD55D0", "#F4465B"), "Upward Trend in Recent Years for Remakes", "The number of movie remake releases by year", "source: List of Film Remakes (Wikipedia)", "https://en.wikipedia.org/wiki/List_of_film_remakes_(A%E2%80%93M)")
```

### Years that inspired the most remakes.
But when were the originals made? **1939** and **1932** was the year with the most movies inspiring remakes with **22** movies in total. If you look at the *5 year rolling average* you can see that the 1930s was the most popular period of cinema we have looked to re-create.

```{r}
originalsByYear <- countByYear(originals)
countByYear_chart(originalsByYear, c("#CFCFCF", "#4A90E2","#4A90E2"), "Downward trend in movies being remade", "The number of original movies released by year with atleast one remake", "source: List of Film Remakes (Wikipedia)", "https://en.wikipedia.org/wiki/List_of_film_remakes_(A%E2%80%93M)")
```

### Too Soon? Years between remakes and originals
How long do filmmakers wait until they remake a movie? Well, looking at the data the averge years between an original movie and a remake is `r round(mean(allMovies$yearsBetween),2)`
```{r}
tooSoon <- allMovies %>% select(remakes_title, remakes_yearsBetween) %>% arrange(desc(remakes_yearsBetween))
tableWithBar(tooSoon, c("Title of Remake", "# of Years after Original"), tooSoon$remakes_yearsBetween, barColour = '#4A90E2')
```

### Again and Again and Again.....
What is the most remade movie?

```{r}
robinHoodData <- allMovies %>%
  distinct() %>%
  filter(originals_key == "Robin Hood (1922)") %>%
  left_join(movieMetaData, by = c("remakes_key" = "key")) %>%
  select(originals_key, remakes_key, remakes_year, imdbrating) %>%
  arrange(remakes_year)

colours <- c("#FBB2BB", "#FF96A3", "#FF6073", "#FF1F3A", "#B90016")
popularRemakes_chart(robinHoodData, colours, "#2. Robin Hood", paste("IMDB Rating for the", nrow(robinHoodData), "remakes of", robinHoodData$originals_key[1]), source = "IMDB", link = "http://www.imdb.com/")

```

```{r}
scroogeData <- allMovies %>%
  distinct() %>%
  filter(originals_key == "Scrooge (1935)") %>%
  left_join(movieMetaData, by = c("remakes_key" = "key")) %>%
  select(originals_key, remakes_key, remakes_year, imdbrating) %>%
  arrange(remakes_year)

colours <- c("#FFD4C3", "#FFA886", "#FF834F", "#EB6431", "#AB4A24", "#7C2706")
popularRemakes_chart(scroogeData, colours, "#1. Scrooge", paste("IMDB Rating for the ", nrow(scroogeData), "remakes of", scroogeData$originals_key[1]), source = "IMDB", link = "http://www.imdb.com/")
```

```{r}
musketeersData <- allMovies %>%
  distinct() %>%
  filter(originals_key == "The Three Musketeers (1921)") %>%
  left_join(movieMetaData, by = c("remakes_key" = "key")) %>%
  select(originals_key, remakes_key, remakes_year, imdbrating) %>%
  arrange(remakes_year)

colours <- c("#C5E0FF", "#A3CDFF", "#77B6FF", "#4A90E2", "#024EA6")
popularRemakes_chart(musketeersData, colours, "#3. The Three Musketeers", paste("IMDB Rating for the", nrow(musketeersData), "remakes of", musketeersData$originals_key[1]), source = "IMDB", link = "http://www.imdb.com/")
```

```{r}
mostRemakes <- mostRemadeMovies(allMovies)
tableWithBar(mostRemakes, c("Title of Remake", "# of Remakes"), mostRemakes$count, barColour = '#FFBE52', pageLength = 10)
```

```{r warning=FALSE}
mostPopularRemakes_data <- mostPopularRemakes(remakes, movieMetaData)
```
### Most Popular Remakes
Which remakes were the most popular? There are a number of movies that don't have ratings on IMDB, but looking at the ones that do, `r mostPopularRemakes_data[1,]$Title` is the most popular remake with a rating of `r mostPopularRemakes_data[1,]$imdbrating`
```{r warning=FALSE}
tableWithBar(data = mostPopularRemakes_data, colNames = c("Movie", "Released", "IMDB Rating"), range = mostPopularRemakes_data$imdbrating, pageLength = 20, barColour = '#F4465B')
```

### Genre
```{r}
genreData <- movieMetaData %>%
  select(genre, imdbrating) %>%
  separate(genre, into = c('primaryGenre', 'secondaryGenre'), extra = 'drop', sep = ",") %>%
  group_by(primaryGenre) %>%
  mutate(averageRating = mean(imdbrating))
  summarise(count = n()) %>%
  mutate(percentage = count/sum(count)*100) %>%
  arrange(desc(count))

sbarChart(genreData)
```

